method

### 2022-02-22 06_Paper/ER-ED/method.Rmd
ignored comment... ;-)
added emg results

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value? -->
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

@@

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
Firstly, SVs will be ordered by magnitude.
Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? AS: Mir ehrlich gesagt erstmal nicht so ... -->

>>>>

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
However, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
Yet we found in accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.

@@

*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

@@

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
Firstly, SVs will be ordered by magnitude.
Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
